oREV item selection and analysis

### 2022-11-24 analysis/orev_item_selection.Rmd
add size comparison with pk values

```{r}
irt_comp_size <- tibble()

@@

  for (i in 10:15) {

@@

    irt_comp_size <- bind_rows(irt_comp_size, row)

    saveRDS(irt_comp_size, "../saves/irt_comp_size.rds")
  }

@@

#saveRDS(irt_comp_size, "../saves/irt_comp_size.rds")

#irt_comp_size <- readRDS("../saves/irt_comp_size.rds")

irt_comp_size%>%
  mutate(ratio = ifelse(elpd_diff == 0,0,ratio))%>%
  pivot_longer(cols = c(ratio, correlation), names_to = "type",values_to = "value")%>% 
  ggplot(aes(x = factor(size), y = value))+
  geom_point(pch = 1)+
  geom_line()+
  facet_grid(type~. , scales = "free_y")+
  theme_bw()+
  labs(x = "No. of items", y = "Comparison value", title = "ratio = abs(elpd_diff)/(2*se_diff)")
```

@@

```{r}
ggsave("../graphs/ICC_1PL_sel.png", height = 6, width = 10, scale = 1)
```

@@

```{r}
dif_sex_guess%>%
  pivot_wider(names_from = sex, values_from = c(mode,uci,lci))%>%
  ggplot(., aes(x = mode_f, y = mode_m))+
  geom_abline(intercept = 0, slope = 1, lty = 1, alpha = .75)+
  geom_point(pch = 1, size = 2, stroke  = 1, aes(col = factor(aoa_german_comb)))+
  geom_linerange(aes(ymin = lci_m, ymax = uci_m),  alpha = .25, lty = 1)+
  geom_linerange(aes(xmin = lci_f, xmax = uci_f),  alpha = .25, lty = 1)+
  geom_text(aes(label = item, x = uci_f +0.2))+
  labs(x = "Group: female", y = "Group: male")+
  scale_color_viridis_d()+
  guides(col = F)+
  theme_few()

@@

```{r}
ggsave("../graphs/dif_cor.png", height = 8, width = 8, scale = 1.2)
```

>>>>

```{r}
#determine_size <- tibble()

@@

  for (i in 21:30) {

@@

    determine_size <- bind_rows(determine_size, row)

    saveRDS(determine_size, "../saves/determine_size.rds")
  }

@@

#saveRDS(determine_size, "../saves/determine_size.rds")

#determine_size <- readRDS("../saves/determine_size.rds")

determine_size%>%
  mutate(ratio = ifelse(elpd_diff == 0,0,ratio))%>%
  pivot_longer(cols = c(ratio, correlation), names_to = "type",values_to = "value")%>% 
  ggplot(aes(x = factor(size), y = value))+
  geom_point(pch = 1)+
  geom_line()+
  facet_grid(type~. , scales = "free_y")+
  theme_bw()+
  labs(x = "No. of items", y = "Comparison value", title = "ratio = abs(elpd_diff)/(2*se_diff)")
```

@@

```{r}
ggsave("../graphs/ICC_1PL_sel.png", height = 6, width = 10, scale = 1, bg = "white")
```

@@

```{r}
dif_sex_guess%>%
  pivot_wider(names_from = sex, values_from = c(mode,uci,lci))%>%
  ggplot(., aes(x = mode_f, y = mode_m))+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = .75)+
  geom_point(pch = 1, size = 2, stroke  = 1, aes(col = factor(aoa_german_comb)))+
  geom_linerange(aes(ymin = lci_m, ymax = uci_m),  alpha = .25, lty = 1)+
  geom_linerange(aes(xmin = lci_f, xmax = uci_f),  alpha = .25, lty = 1)+
  geom_text(aes(label = item, x = uci_f +0.2))+
  labs(x = "Group: female", y = "Group: male")+
  scale_color_viridis_d()+
  guides(col = F)+
  coord_fixed()+
  theme_few()

@@

```{r}
ggsave("../graphs/dif_cor.png", height = 6, width = 6, scale = 1.2)
```
